\documentclass{my_cv}
\usepackage{multicol}
\setlength{\multicolsep}{4.0pt}
\begin{document}


\newcommand\blfootnote[1]{%
  \begingroup
  \renewcommand\thefootnote{}\footnote{#1}%
  \addtocounter{footnote}{-1}%
  \endgroup
}

\name {Alexander Chung}

\address{5042 45\textsuperscript{th} Avenue}{Delta, British Columbia, Canada}{V4K 1K3}

\contact {alex.chung@mail.mcgill.ca}{(514) 914 8374}

\section{Education}
\datedsubsection{McGill University}{2013-2017}
B.A. Computer Science, Minor Mathematics \& Economics
\section{Work Experience}

\datedsubsection {\textit{Lead Backend Developer} - Nimbus Inc.}{2017}
	\workitems
	{Created, tested and deployed the backend server for the WakeUp app. Managed and led the development team until completion.}
	{Amongst other things, I implemented a database supporting numerous search criteria, an automated email sending service, a secure user authentication system, and designed a fault tolerant push notification system.}
\datedsubsection {\textit{Contributor} - Puppeteer, Open Source Google Project}{2017}
	\workitems
	{Added functionality, wrote integration tests, and passed Google standards.}
	{Puppeteer is an API for headless chrome.}
\datedsubsection{\textit{Chief Technical Officer and Webmaster} - McGill Ambassador Program}{2016-2017}
	\begin{itemize}
		\item Designed and maintained a website as part of a McGill pilot program intended to amalgamate information for students.
		\item Attended weekly meetings with McGill staff and peers, ensuring key information was translated to the website and updated in a timely manner.
		\item Created visual content, such as advertisement and promotional stickers, as a graphic designer.
	\end{itemize}
\datedsubsection {\textit{Computer Science, Economics, and Mathematics Tutor} - McGill}{2013-2017}
	\begin{itemize}
	\item Provided aid in courses including Programming Languages and Paradigms, Discrete Structures 2, Artificial Intelligence, Algorithms and Data Structures, Intro to Computer Science.
	\end{itemize}

\section{Core Competencies}

\subsection{Programming Languages and Theory}
%\begin{tabularx}{\textwidth}{ r c c l }
\begin{multicols}{4}
	\begin{itemize}
		\item Machine Learning 
		\item Computational Theory 
		\item Discrete Math
		\item Linear Algebra
		\item Databases
		\item Network Protocols
		\item Unity Game Dev
		\item JavaScript
		\item C\#
		\item C
		\item Python 
		\item Java 
	\end{itemize}
\end{multicols}
 %\end{tabularx}


\subsection{Creative Aptitude}
	\workitems
	{Received the Michael Dunne Art Award and Scholarship upon graduation of high school in 2013.}
	{Created logos, posters, and advertisements for numerous clubs, shows, companies, and more throughout high school and university.}


\section {Supporting Documentation}
\begin{labeling}{}
\item [Code Repository:] http://www.github.com/AlexChung1995
\item [Artistic Portfolio:] http://www.alexcchung.carbonmade.com
\end{labeling}
%\section{References}
%\subsection{Salman Memon - \normalsize \underline{salman.memon@mail.mcgill.ca}}
%\begin{itemize}
%	\item{Graduate Student, McGill University}
%	\item{My research project supervisor.}
%\end{itemize}
%\subsection{William Liu - \normalsize \underline{william.liu@nimbusapp.ca}}
%\begin{itemize}
%	\item{CEO, Nimbus Education inc.}
%	\item{Worked together to develop the Nimbus and WakeUp apps.}
%\end{itemize}


\section {Personal}
	\begin{itemize}
	\item Avid snowboarder and swimmer.
	\item Artist and painter.
	\end{itemize}



\blfootnote{References available upon request.}
\end{document} 